Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-06-04 paper/sec-mva.tex
more work on mva sec

In Figure~\ref{fig:exampleroc} the ROC curves for the two analyses are shown, demonstrating that the neural network is able to
perform well in both cases. Figure~\ref{fig:nnweights} shows the distribution of NN weights in both cases.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{plots/nnweights_res.pdf}
\includegraphics[width=1\textwidth]{plots/nnweights_boost.pdf}
\caption{Distribution of weights per input variable in the final ANN analysis. The above figure shows the weight distribution in the case of the resolved analysis, while the lower plot shows the boosted analysis.}
\label{fig:nnweights}
\end{center}
\end{figure}
\clearpage

>>>>

In Fig.~\ref{fig:exampleroc} the ROC curves for the
boosted, intermediate and resolved categories are found.
%
As could already be inferred from the distribution of neural
networks output in Fig.~\ref{fig:nnresponse}, we find
that the neural network MVA is reasonably efficient
in discriminating signal over background.
%
The performance is slightly better in the case of the boosted
topology, in particular thanks to the information provided
by the substructure variables.
%
In both cases we see that with a moderate reduction of signal
efficiency of $\sim 0.8$, one can reduce the background by 80\%,
which translates into an improvement factor of the pre-MVA $S/\sqrt{B}$
of almost $\sim 1.8$.

@@

In order to gain physical insight of which are the variables that
contribute the most to the MVA discrimination it is useful
to show the distribution of NN weights for each of the
input variables.
%
This distributions is a measure of the correlation between
each input variable and the Neural Network output: the higher
the value, the stronger the impact of this variable in
separating signal from the background.
%
In Fig.~\ref{fig:nnweights} we show
the distribution of NN weights for the resolved and boosted categories.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.48\textwidth]{plots/nnweights_res.pdf}
\includegraphics[width=0.48\textwidth]{plots/nnweights_boost.pdf}
\caption{\small Distribution of weights per input variable in the final ANN analysis. The above figure shows the weight distribution in the case of the resolved analysis, while the lower plot shows the boosted analysis.}
\label{fig:nnweights}
\end{center}
\end{figure}
\clearpage
